Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-04 manuscript-chicago.Rmd
Fix references

# Discussion
In the present study, we investigated the dynamics of real-world events and
online communication on Twitter in Syria during Arab Spring. CRQA methodology
allows us to disentangle the relationship between sociolinguistic cohesion and
exogenous political events. This work stands alongside the model of
Palestinian-Israeli social media and events developed by Zeitzoff (2011), and
the role of peripheral participants in the Syrian Arab Spring movement by
Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we
demonstrate how language and social mobilization interact with events along the
conflict-cooperation continuum in Syria. We have introduced a novel theoretical
framework of sociolinguistic cohesion which we operationalize using a weighted
measure of lexical relationships. We examined how virtual and physical social
mobilization evolve over time in tandem. Using nonlinear dynamical time series
analyses, we investigated the theory that virtual mobilization is increasingly
reflective of real-world events during times of strife.

>>>>

# Discussion
In the present study, we investigated the dynamics of real-world events and
online communication on Twitter in Syria during Arab Spring. CRQA methodology
allows us to disentangle the relationship between sociolinguistic cohesion and
exogenous political events. This work stands alongside the model of
Palestinian-Israeli social media and events developed by @zeitzoff2017social, and
the role of peripheral participants in the Syrian Arab Spring movement by
@steinert2017spontaneous. By introducing the CRQA and WCRQA methods, we
demonstrate how language and social mobilization interact with events along the
conflict-cooperation continuum in Syria. We have introduced a novel theoretical
framework of sociolinguistic cohesion which we operationalize using a weighted
measure of lexical relationships. We examined how virtual and physical social
mobilization evolve over time in tandem. Using nonlinear dynamical time series
analyses, we investigated the theory that virtual mobilization is increasingly
reflective of real-world events during times of strife.
